Geospatial and Temporal Analysis of Toronto's Cycling Infrastructure

### 2024-09-24 paper/paper.qmd
paper references updated

Data used in this paper was cleaned, processed, modeled and tested with the programming language R [@citeR]. Also with support of additional packages in R: `sf` [], `readr` [@citeReadr], `ggplot2` [@citeGgplot], `osmdata` [], `tidyverse` [@citeTidyverse], `jsonlite` [], `dplyr` [@citeDplyr], `here` [], `knitr` [], `kableExtra` [], `` [], `` [], .

>>>>

Data used in this paper was cleaned, processed, modeled and tested with the programming language R [@citeR]. Also with support of additional packages in R: `sf` [@citeSf], `readr` [@citeReadr], `ggplot2` [@citeGgplot2], `osmdata` [@citeOsmdata], `tidyverse` [@citeTidyverse], `jsonlite` [@citeJsonlite], `dplyr` [@citeDplyr], `here` [@citeHere], `knitr` [@citeKnitr], `kableExtra` [@citeKableExtra].
